---
title: "gaussianComparisons - Final Report"
author: "Tyler Brandt, Rohan Gupta, Marcus Hallman, Gangyi Sun"
date: "29/04/2018"
output: html_document
---

## Objetive of Project 

The data we are working with has to do with user impressions of movie reviews. Users have been shown sets of two comparisons and were asked to pick which one was more positive. If this process is done enough times, you can figure out the order of most positive or negative reviews that you showed the users. The goal of this project is to figure out which two reviews you want to show the next user. By using the [Gaussian Process](http://www.gaussianprocess.org/gpml/chapters/RW.pdf) described by Williams and Rasmussen, we determined the expected information gained by asking the user to choose between two specific reviews. Our maxInfoComp function will make a recommendation for the largest information gain given the data you already have.



## List of all Functions Created 

For a list of all functions used in this pacakage and the purpose they serve, refer to README. 



## Sample Dataset 

The sample dataset is composed of comparisons done on movie reviews. "Comparison" denotes which comparison is being referenced in a given row. "Document" denotes which document is being compared, and "Result" is 1 if the document was more positive than its counterpart. We clean the dataset by placing each compared pair on the same line coding result 1 if the first review was deemed more positive and -1 if the second was deemed more positive.



## Sample Results for Doc ID 5059 
**Please set your own working directory in line 39.
**The XQuartz package (install from https://www.xquartz.org) is requried for this part of the markdown to compile. 

We compare docid 5059 to all other documents in our sample dataset. 

```{r, echo=FALSE,message=FALSE}

## Load libraries
library(devtools)
library(roxygen2)

## Set Working Directory 
setwd("~/Documents/GitHub/ASP_group_project") # SET YOUR OWN WORKING DIRECTORY 

## Load in package 
current.code <- as.package("gaussianComparisons")
load_all(current.code)

## Comparing docid 5059 to all other documents to determine which comparisons will be most informative
data_montgomery <- read.csv("gaussianComparisons/data/exampleHITs.csv")
data_small <- read.csv("gaussianComparisons/data/exampleHITsSmall.csv")
data_clean <- cleaner(data_montgomery)
omega_data <- omega(data_montgomery,2)
docids <- unique(data_montgomery$document_id)

# Create s values
finalS_values <- NULL
for (i in docids){
  new_Svalue <- finalS(doc1 = 5059, doc2 = i, omega1 = omega_data, cleaned_data = data_clean,
                       sigma = 2, tolerance = 0.01)
  finalS_values <- c(finalS_values, new_Svalue)
}

# Create mu hat values
mu_values <- NULL
sigma <- 2
for (i in docids){
  little_omega <- rep(0, nrow(data_clean))
  for (j in 1:nrow(data_clean)){
    if (5059 == data_clean$first[j]){
      little_omega[j] <- little_omega[j] + sigma^2
    }
    if (5059 == data_clean$second[j]){
      little_omega[j] <- little_omega[j] - sigma^2
    }
    if (i == data_clean$first[j]){
      little_omega[j] <- little_omega[j] - sigma^2
    }
    if (i == data_clean$second[j]){
      little_omega[j] <- little_omega[j] + sigma^2
    }
  }
  new_muvalue <- muMaker(doc1 = 5059, doc2 = i, omega1 = omega_data, cleaned_data = data_clean,
                         sigma = 2, tolerance = 0.01, little_omega = little_omega)
  mu_values <- c(mu_values, new_muvalue)
}

# Create rho squared values
rhoSquared_values <- NULL
sigma <- 2
for (i in docids){
  little_omega <- rep(0, nrow(data_clean))
  for (j in 1:nrow(data_clean)){
    if (5059 == data_clean$first[j]){
      little_omega[j] <- little_omega[j] + sigma^2
    }
    if (5059 == data_clean$second[j]){
      little_omega[j] <- little_omega[j] - sigma^2
    }
    if (i == data_clean$first[j]){
      little_omega[j] <- little_omega[j] - sigma^2
    }
    if (i == data_clean$second[j]){
      little_omega[j] <- little_omega[j] + sigma^2
    }
  }
  new_rhoSquaredValue <- rhoSquaredMaker(doc1 = 5059, doc2 = i, omega1 = omega_data,
                                         cleaned_data = data_clean, sigma = 2, tolerance = 0.01,
                                         little_omega = little_omega)
  rhoSquared_values <- c(rhoSquared_values, new_rhoSquaredValue)
}

```

The s, mu_hat and rho_squared values are reported, in descending values of s.
We can see that there there is a strong correlation (R-squared = 0.9796) between s_values and exp(mu_hat).
```{r, echo=FALSE}
# Create dataframe
summary_df <- data.frame(rep(5059, 50), docids, finalS_values, mu_values, rhoSquared_values)
colnames(summary_df) <- c("doc1", "doc2", "s_values", "mu_hat", "rho_squared")
summary_df <- summary_df[order(summary_df$s_values), ]
head(summary_df)

## Plot s values versus mu hat
expEstMu<-lm(summary_df$s_values ~ exp(summary_df$mu_hat))
plot(summary_df$mu_hat, summary_df$s_values, xlab = "mu hat values", ylab = "s values",
     main = "Information Gain By Expected g Values")
lines(summary_df$mu_hat,predict(expEstMu),col='red')

## Plot s values versus rho squared hat
plot(summary_df$rho_squared, summary_df$s_values, xlab = "rho^2 values", ylab = "s values",
     main = "Information Gain By Expected Variance Values")

``` 




