---
title: "gaussianComparisons - Final Report"
author: "Tyler Brandt, Rohan Gupta, Marcus Hallman, Gangyi Sun"
date: "29/04/2018"
output: html_document
---

## Objetive of Project 

The data we are working with has to do with user impressions of movie reviews. Users have been shown sets of two comparisons and were asked to pick which one was more positive. If this process is done enough times, you can figure out the order of most positive or negative reviews that you showed the users. The goal of this project is to figure out which two reviews you want to show the next user. By using the [Gaussian Process](http://www.gaussianprocess.org/gpml/chapters/RW.pdf) described by Williams and Rasmussen, we determined the expected information gained by asking the user to choose between two specific reviews. Our maxInfoComp function will make a recommendation for the largest information gain given the data you already have.

```{r}



```


## List of all Functions Created 

For a list of all functions included and used in this pacakage, refer to README. 


## Sample Dataset 

The sample dataset is composed of comparisons done on movie reviews. "Comparison" denotes which comparison is being referenced in a given row. "Document" denotes which document is being compared, and "Result" is 1 if the document was more positive than its counterpart. We clean the dataset by placing each compared pair on the same line coding result 1 if the first review was deemed more positive and -1 if the second was deemed more positive.

```{r}



```


## Sample Results for Doc ID 5059 

```{r}



```

